\cvsection{Employment}
\begin{cventries}

%---------------------------------------------------------
  \cventrypara
  {Senior Software Engineer} % Job title
  {OVO Energy} % Organization
  {Bristol} % Location
  {2016  - Present} % Date(s)
  {I currently work for OVO group within their Kaluza business building a new real-time intelligent energy platform for
  utilities to manage a modern renewable energy grid. I've worked on it since its inception and have been central in designing
  and implementing some of its core event streaming microservices on top of Apache Kafka.}
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Most recently I've been working on parsing industry data (flows) building software to act as a bridge for
      translating millions of energy industry transactions files onto Kafka and vice-versa back to the industry. Clojure
      despite the lack of a type system has been a great tool for this task.}
      \item {Core developer on Kaluza's real-time charging pipeline, a collection of Clojure microservices backed by
      kafka that spans taking customer meter readings through to billing customers based on contract length and tariff.
      This has been my main focus for my time at Ovo and many of my own ideas and design decisions have been incorporated
      into the design}
      \item {Implemented a 3rd party payment integration for an online credit card payment system, written in Scala using
      ScalaZ and http4s}
    \end{cvitems}
  }

  \cventrypara
  {Senior Software Engineer} % Job title
  {LINE Corporation - MixRadio} % Organization
  {Bristol} % Location
  {2014  - 2016} % Date(s)
  {With MixRadio being sold to LINE corporation by Microsoft my role was a continuation from that at Microsoft.}
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {I developed a full stack Clojure and ClojureScript service which enabled in house mixmasters to manually
      tweak MixRadio's recommendations engine.}
      \item {I Integrated SalesForce with MixRadio’s internal CRM system. A Clojure service which extracted all
      relevant data from Salesforce and parsed it to AWS SQS and persisted it to Redshift.}
      \item {I produced an EMR processing pipeline to transform our massive user taste profiles into a suitable
      format and export it to SalesForce for recommendation emails.}
      \item {I wrote various Cascalog and Pigpen Big data flows over millions of user events to support and improve
      music recommendations eg find and boost emerging “hot” tracks.}
    \end{cvitems}
  }

  \cventrypara
  {Senior Software Engineer} % Job title
  {Microsoft - MixRadio} % Organization
  {Bristol} % Location
  {2013  - 2014} % Date(s)
  {Microsoft purchased Nokia's mobile business. My work was focused even more on the core music recommendations of
  the business building fault-tolerant, performant Clojure services and data processing at scale.}
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Played a key role in creating a complex music recommendation service for similarly liked tracks and artists.
      This replaced the 3rd party reliance on The EchoNest. Built with Clojure on DynamoDB.}
      \item {I built a highly performant microservice to match track and artist metadata to MixRadios internal representation.}
      \item {I created a service to warehouse client user events from Kafka to S3, encrypting any sensitive user data.}
      \item {I designed and produced a service to produce new album release events no notify interested users,
        in Clojure on MongoDB.}
      \item {I built up the majority of MixRadios client ’views’ API, it produced customised views of JSON data
      allowing clients to build their pages, coded in Java and Spring.}
      \item {A key contributor to MixRadios core services:
        \begin{itemize}
          \item Users music taste profile service, based on MongoDB in Clojure.
          \item An API to serve session based curated mixes, in Clojure and Redis.
          \item The music catalogue and search engine, based on Java, MySQL and Apache Solr.
        \end{itemize}}
    \end{cvitems}
  }

  \cventrypara
  {Senior Software Engineer} % Job title
  {Nokia} % Organization
  {Bristol} % Location
  {2009  - 2013} % Date(s)
  {During my time at Nokia I transitioned from a Java and linux build engineer, to a Clojure engineer. My role from newest to oldest:}
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {\emph{Developer:} Designed and built key services to provide mobile phone notifications to millions of users.}
      \item {\emph{Developer:} In 2011, I joined a small team working on Nokia's first production Clojure services with the ultimate aim to replace our 3rd party integration with The EchoNest.}
      \item {\emph{Developer:} Nokia ceased to support Meego and I moved into full-time Java development. I was one-half of a pair that integrated with a 3rd party company, The EchoNest.
      Integrating their music recommendations produced Nokia music’s first iteration of its internet radio (later to be called MixRadio). This was a Java and Spring based service.}
      \item {\emph{Build Manager:} I became the Bristol office's package manager for Nokia's Meego (Linux-based) operating system.
      I was responsible for automating the build process and integrating Bristol's music software into the wider companies operating system via apt package management.}
    \end{cvitems}
  }

  \cventry
  {Senior Automation Engineer} % Job title
  {Alterian} % Organization
  {Bristol} % Location
  {2008  - 2009} % Date(s)
  {A UK-based supplier of marketing automation software and services. I was their sole automated tester and worked on
  their “Next Generation” web-based platform.}

  \cventry
  {Senior Automation Engineer} % Job title
  {Experian (Decision Analytics EMEAI)} % Organization
  {Bristol} % Location
  {2006  - 2008} % Date(s)
  {Talgentra was acquired by Experian, I progressed into a more senior automated testing role.}

  \cventry
  {Junior Software Engineer} % Job title
  {Talgentra} % Organization
  {Bristol} % Location
  {2004 - 2006} % Date(s)
  {Talgentra produced utility billing software for electricity, water, gas and telecommunications. This was my initial introduction to Java, writing some Junit and automated acceptance tests.
  }
\end{cventries}
